\documentclass[a4paper,12pt]{article}
\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\begin{document}

\pagestyle{empty}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Naresh Bhosale} \\[7.5pt]
\href{https://github.com/WebNaresh}{\raisebox{-0.05\height}\faGithub\ WebNaresh} \ $|$ \
\href{https://www.linkedin.com/in/naresh-bhosale-173145265/}{\raisebox{-0.05\height}\faLinkedin\ Naresh Bhosale} \ $|$ \
\href{mailto:bhosalenaresh73@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ nareshbhosale73@gmail.com} \ $|$ \
\href{tel:+919370928324}{\raisebox{-0.05\height}\faMobile \ +919370928324} \\
\end{tabularx}

\vspace{1cm}

[Date]

\vspace{1cm}

Dear Hiring Manager,

I am excited to apply for the [Position Name] position at your esteemed organization. With a strong foundation in frontend development and a passion for creating user-centered designs, I am eager to contribute my skills and experience to your team.

In my previous role as a Software Engineer Intern, I developed responsive and dynamic web applications using React and Next.js, integrated frontend applications with backend systems using Node.js, and designed intuitive and engaging user interfaces. These experiences have honed my ability to create seamless and interactive user experiences, which I am eager to bring to your organization.

My portfolio includes various projects, such as the "Expense\_Tracker" built in C++, which features categorization, expense charts, and theming options. This project demonstrates my ability to develop complex and user-friendly applications. Additionally, my work on the AEGIS system, both frontend and backend, showcases my expertise in JavaScript and my commitment to building robust and scalable systems.

I am currently pursuing a Master's in Computer Application at SPPU, where I continue to expand my knowledge and stay up-to-date with the latest industry trends and best practices. My strong problem-solving skills, coupled with my ability to work collaboratively in team settings, make me a valuable asset to any development team.

I am particularly drawn to this opportunity because of your company's commitment to innovation and excellence in user experience. I am confident that my background and skills align well with the needs of your team, and I am eager to bring my passion for design and development to your organization.

Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to the success of your team. Please feel free to contact me at +91 9370928324 or via email at \href{mailto:nareshbhosale73@gmail.com}{nareshbhosale73@gmail.com}.

\vspace{1cm}

Sincerely, \\
Naresh Bhosale

\end{document}
