\documentclass[a4paper,12pt]{article}
\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\begin{document}

% Non-numbered pages
\pagestyle{empty}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Naresh Bhosale} \\[7.5pt]
\href{https://github.com/WebNaresh}{\raisebox{-0.05\height}\faGithub\ WebNaresh} \ $|$ \
\href{https://www.linkedin.com/in/naresh-bhosale-173145265/}{\raisebox{-0.05\height}\faLinkedin\ Naresh Bhosale} \ $|$ \
\href{mailto:bhosalenaresh73@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ nareshbhosale73@gmail.com} \ $|$ \
\href{tel:+919370928324}{\raisebox{-0.05\height}\faMobile \ +919370928324} \\
\end{tabularx}

\section{Summary}
Aspiring Interaction Designer with a strong foundation in frontend development and a passion for creating user-centered designs. Experienced in prototyping, UX/UI design, and enhancing user experiences through intuitive interfaces. Currently working on projects that emphasize user interaction and design, with a commitment to learning and applying best practices in User-Centered Design (UCD).

\section{Work Experience}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{Software Engineer Intern} & \hfill Aug 2023 - Present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
   \begin{itemize}[nosep, after=\strut, leftmargin=1em, itemsep=3pt]
 \item[--] Developed responsive and dynamic web applications using React and Next.js.
 \item[--] Integrated frontend applications with backend systems using Node.js.
 \item[--] Designed intuitive and engaging user interfaces, improving user experience and interaction.
 \item[--] Created prototypes to test and validate design concepts, incorporating user feedback into iterative design processes.
\end{itemize}
\end{minipage}
}
\end{tabularx}

\section{Projects}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{Expense\_Tracker} & \hfill \href{https://github.com/WebNaresh/Expense_Tracker}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{A C++ project for tracking expenses, featuring categorization, expense charts, and theming options.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{AEGIS\_FRONTEND} & \hfill \href{https://github.com/WebNaresh/AEGIS_FRONTEND}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{JavaScript project for the frontend of the AEGIS system, providing an intuitive UI for users.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{AEGIS\_BACKEND} & \hfill \href{https://github.com/WebNaresh/AEGIS_BACKEND}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{JavaScript project for the backend of the AEGIS system, ensuring robust data handling and API integration.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{flutter\_quiz\_app} & \hfill \href{https://github.com/WebNaresh/flutter_quiz_app}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{C++ project for a quiz application built with Flutter, offering a seamless and engaging user experience.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{rmtft-package} & \hfill \href{https://github.com/WebNaresh/rmtft-package}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{JavaScript package for integrating RMTFT functionality, enhancing application performance.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{rmtft} & \hfill \href{https://github.com/WebNaresh/rmtft}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{TypeScript project focusing on advanced RMTFT features for improved user interaction.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{flutter-second-app} & \hfill \href{https://github.com/WebNaresh/flutter-second-app}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{C++ project for a Flutter application, demonstrating advanced UI/UX design principles.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{first-flutter-test-app} & \hfill \href{https://github.com/WebNaresh/first-flutter-test-app}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{C++ project for a test application built with Flutter, showcasing foundational skills in mobile development.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{vite-react-app-mui-tailwindcss--integrate} & \hfill \href{https://github.com/WebNaresh/vite-react-app-mui-tailwindcss--integrate}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{JavaScript project integrating Vite, React, and Tailwind CSS for efficient and responsive web development.} \\
\end{tabularx}

% Add more projects here following the same format

\section{Education}
\begin{tabularx}{\linewidth}{@{} l X @{}}
2023 - present & MCA (Master Of Computer Application) at \textbf{SPPU} \hfill (GPA: Present) \\

2020 - 2023 & Bachelor's of Computer Application at \textbf{Shivaji University} \hfill (GPA: 8.0/10.0) \\

2020 & Class 12th HSC Board \hfill (B) \\

2018 & Class 10th SSC Board \hfill (A) \\
\end{tabularx}

\section{Skills}
\begin{tabularx}{\linewidth}{@{} l X @{}}
Design \& Development Tools & \normalsize{Figma, Adobe XD, Sketch, React JS, Tailwind CSS, Next JS, React Native, Flutter} \\
UX Skills & \normalsize{Prototyping, Wireframing, User Research, Usability Testing, User-Centered Design (UCD)} \\
Additional Skills & \normalsize{Problem Solving, Communication, Team Collaboration, Creative Thinking} \\
\end{tabularx}

\section{NPM Packages}
\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{phonepe-payment-integration package (npm)} & \hfill \href{https://www.npmjs.com/package/phonepe-payment-integration}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Facilitates the integration of the PhonePe payment gateway into applications, streamlining the process of handling payments.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} l r @{}}
\textbf{mui-tailwind-react-combine library (npx)} & \hfill \href{https://www.npmjs.com/package/react-mui-tailwind_css_frontend}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{A library that combines React, MUI, and Tailwind CSS, simplifying frontend development and styling.} \\
\end{tabularx}

% Add more NPM packages here following the same format

\end{document}
